---
title: "MIS581_Profolio_porject"
author: "Lokesh Prabakaran"
date: "May 7, 2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

setwd('/Users/czlxp/Desktop/Lokesh/CSU_Global/Assiggnments/MIS581_Capstone_ BIDA')
library(gains)
library(e1071)
library(MASS)
library(pROC)
library(ROCR)
library(rpart)
library(rpart.plot)
library(caret)
library(tidyverse)
library(tidyr)
library(stats)

```
**Import the dataset into R.**

```{r}

churn <- read.csv("Telco_Customer_Churn.csv")


```
**Display the structure of the dataset.**

```{r}

str(churn)


```

**Summary of the dataset.**

```{r}

summary(churn)


```

**Count number of NAs in the  dataset**

```{r}

colSums(is.na(churn))

```
**print the column names in list**

```{r}

t(t(names(churn)))


```
**Display first 5 observations of the dataset.**

```{r}

head(churn, 5)


```

**Displaying dataset dimension.**

```{r}

dim(churn)


```
```{r}
# Removing NAs 

churn=na.omit(churn)
```

```{r}
# Removing CustomerID variable

churn$customerID=NULL
```
```{r}
# Changing Gender into factor variable

churn$gender=as.factor(churn$gender)
```
```{r}
# Changing SeniorCitizen into factor variable

churn$SeniorCitizen=as.factor(churn$SeniorCitizen)
```
```{r}
# Changing Partner into factor variable

churn$Partner=as.factor(churn$Partner)
```
```{r}
# Changing Dependents into factor variable

churn$Dependents=as.factor(churn$Dependents)
```
```{r}
# Changing Churn into integer variable

churn$tenure=as.integer(churn$tenure)
```
```{r}
# Changing phoneServices into factor variable

churn$PhoneService=as.factor(churn$PhoneService)
```
```{r}
# Changing multipleLines into factor variable

churn$MultipleLines=as.factor(churn$MultipleLines)
```
```{r}
# Changing InternetService to factor variable

churn$InternetService=as.factor(churn$InternetService)
```

```{r}
# Two-Sample t-test for numerical variables.

t.test(tenure ~ Churn, data = churn)

t.test(MonthlyCharges ~ Churn, data = churn)

t.test(TotalCharges  ~ Churn, data = churn)

```

```{r}
# Chi-Square t-test for numerical variables.

chisq.test(table(churn$Churn, churn$SeniorCitizen))
chisq.test(table(churn$Churn, churn$Dependents))

```